---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# randbn

<!-- badges: start -->
<!-- badges: end -->


This repository contains a small R-package with function I use frequently to draw random Bayesian networks. It is based on routines provided in the `pcalg` and `bnlearn` package.


## Installation

You can install the development version of randbn from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("verahk/randbn")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(randbn)

r <- 007           # seed number
n <- 3             # number of nodes
d <- 1             # expected number of neighbours
nlev <- rep(2, n)  # cardinality of each variable

set.seed(r)
bn <- rand_bn(n, d, "cat", nlev = nlev, alpha = 1)
bn
```
Replicate with the distinct functions:
```{r}
set.seed(r)
dag  <- rand_dag(n, d) # draw an adjacency matrix 
dist <- rand_dist(dag, "cat", nlev = nlev, alpha = 1)  # draw set of local dist
bn1  <- custom_bn(dag, dist, use_bnlearn = FALSE)       # construct bn.fit() object
all.equal(bn1, bn)
```

## Example 2: Add intervention node to bn 
```{r}

dag <- matrix(0, 2, 2)
dag[1, 2] <- 1
dist <- rand_dist(dag, "cat", nlev = rep(2, ncol(dag)), alpha = 1)
bn <- custom_bn(dag, dist)

# generate a new intervention node to produce an augmented network
node <- new_node("I", children = "X2", prob = array(1:0, 2, list(I = c("off", "on"))))
ls.str(node)

# imperfect intervention: 
# - draw local intervention distributions from a uniform Dirichlet
bn_augmented <- add_node_to_bn(bn, node)
bn_augmented$X2

# almost-perfect intervention: 
# - draw local intervention distributions from a the same, skewed Dirichlet
mu <- c(.9, .1)
ess <- 1000
bn_augmented <- add_node_to_bn(bn, node, alpha = mu*ess)
bn_augmented$X2

# perfect intervention: deterministic local intervention distributions 
generate_local_dist <- function(dims) {
  new_rows <- array(0,  dims)
  for (ss in 1:(dims[3]-1)) new_rows[ss,,ss] <- 1
  return(new_rows)
}
bn_augmented <- add_node_to_bn(bn, node, generate_local_dist = generate_local_dist)
bn_augmented$X2

```




